borrow-lambda

### 2025-04-19 paper/paper.tex
oops typo
typos

For the syntax of types, we first introduce a couple of constructs that will make
them up.
\begin{center}
    \begin{bnf}
        $\kappa$ : \textsf{Lifetime} ::= $\alpha$
    \end{bnf}

@@

\begin{figure}[h]
    \begin{lstlisting}[language=caml]
        let a = 0 in        (* a has lifetime '0 *)
        let b = succ 0 in   (* b has lifetime '1 *)
        let c = (\d. d) in  (* c has lifetime '2 *)
        let d = &b in       (* b has type &'1 nat *)
        let d = &mut a in   (* b has type &'0 mut nat *)
        ...
    \end{lstlisting}

@@

A couple of interesting special cases include the handling of if statements,
and providing the ability to assign a value to a variable that has had a value
moved out of it. In the former case (T-If), we will output the union of both $\Delta$
contexts generated by traversing each branch of the if statement. In the latter case (T-Assign),
we remove the current variable from the $\Delta$ context when assigning it a value
if it is present, so that it can be used again, as seen in the following rule.

@@

\section{Conclusion and Future Work}
The language we implemented captures the basic ideas of ownership and borrow checking like in Rust, however it is quite limited in scope. It is useful from a theoretical standpoint to formally understand the semantics of borrowing, but
it is certainly not useful for practical programming. There are many areas in which we could make big improvements in terms of usability:

>>>>

For the syntax of types, we first introduce a couple of constructs that will make
them up. This syntax is based on a paper by Jung et al. (2018) \cite{rustbelt1}.
\begin{center}
    \begin{bnf}
        $\kappa$ : \textsf{Lifetime} ::= $\alpha$
    \end{bnf}

@@

\begin{figure}[h]
    \begin{lstlisting}[language=caml]
        let a = 0 in        (* a has lifetime '0 *)
        let b = succ 0 in   (* b has lifetime '1 *)
        let c = (\d. d) in  (* c has lifetime '2 *)
        let d = &b in       (* d has type &'1 nat *)
        let e = &mut a in   (* e has type &'0 mut nat *)
        ...
    \end{lstlisting}

@@

A couple of interesting special cases include the handling of conditionals,
and providing the ability to assign a value to a variable that has had a value
moved out of it. In the former case (T-If), we will output the union of both $\Delta$
contexts generated by traversing each branch of the conditional. In the latter case (T-Assign),
we remove the current variable from the $\Delta$ context when assigning it a value
if it is present, so that it can be used again, as seen in the following rule.

@@

\section{Conclusion and Future Work}
The language we implemented captures the basic ideas of ownership and borrow checking like in Rust, however it is quite limited in scope. It is useful from a theoretical standpoint to formally understand the semantics of borrowing, but
it is certainly far from practical programming. There are many areas in which we could make big improvements in terms of usability:
